Application-Level Regression Testing Framework using Jenkins

### 2017-03-13 manuscript/manuscript.tex
Added short abstract

\begin{abstract}
This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters. Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service. We evaluated test frameworks such as Inca [1] and Jenkins [2]. Jenkins was chosen for its versatility, large user base, and multitude of plugins including plotting test results over time. We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). Not only does Jenkins have the ability to store historical data but it can also send customized notifications (e.g. send email or text pages) based on the result of a test. Some of the requirements we had include two-factor authentication to access Jenkins GUI with privileges to execute tests and account management through LDAP. In this paper we describe our implementation of these requirements to ensure a secure and usable deployment of a Jenkins instance.

@@

\subsection{Introduction to Jenkins}
Jenkins [2] is a self-contained, open source automation server which can be used to automate all sorts of tasks such as building, testing, and deploying software. Jenkins can be installed through native system packages, Docker, or even run standalone by any machine with the Java Runtime Environment installed. 
To install from rpm as root:
wget -O /etc/yum.repos.d/jenkins.repo http://pkg.jenkins-ci.org/redhat/jenkins.repo
rpm --import https://jenkins-ci.org/redhat/jenkins-ci.org.key
yum install jenkins
\subsection{Master-Node Configuration}
We added a standard user account to our cluster that will execute the Jenkins tests. Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.  The keys on the server are located in Jenkins home directory (/var/lib/jenkins/.ssh). Using the GUI management console, the keyfile location and passphrase was entered under Manage Jenkins, Configure System, SSH remote hosts section. A unique SSH site is configured for our TDS, production and development login nodes.

@@

\subsection{Configuration Choices}
Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restricting access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.  A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console. All the configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted. \\
(config file snippets below)

\begin{lstlisting}
/etc/ssh/sshd_config:
Match Host bwbh1.ncsa.illinois.edu,
bwbh2.ncsa.illinois.edu
HostbasedAuthentication yes

@@

/etc/httpd/conf.d/ssl.conf:
Listen 443
<VirtualHost _default_:443>
SSLSessionCache         shmcb:/var/cache/mod_ssl/scache
SSLSessionCacheTimeout  300
ServerName bwjenkins.ncsa.illinois.edu:443
 # -- The following sets ReverseProxy for Jenkins
  ProxyRequests       Off
  ProxyPreserveHost   On
  AllowEncodedSlashes On
  <Proxy *>
    Order deny,allow
    Allow from all
  </Proxy>
  ProxyPass       / http://localhost:8080/ nocanon
  ProxyPassReverse / http://localhost:8080/
  ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
  RequestHeader set X-Forwarded-Proto "https"
  RequestHeader set X-Forwarded-Port "443"

  DefineExternalAuth pwauth+session pipe /usr/local/bin/
  pwauth+session
  <LocationMatch / > 
    AuthType Basic
    AuthBasicProvider external
    AuthName "NCSA RSA OTP login" 
    AuthExternal pwauth+session
    require valid-user

@@

  </LocationMatch>
\end{lstlisting}

\subsection{LDAP with Jenkins}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

@@

\section{Conclusion}
\subsection{caveats}
Transient errors with Jenkins sometimes occur--particularly with the Jenkins ssh subsystem.  It's not unusual to get failure rates of 1/100 from an ssh failure which is completely transient (immediately running the test again manually clears the issue on the dashboard).
\label{sec:conclusion}

% use section* for acknowledgement
\section*{Acknowledgment}
This research used resources at the National Institute for Computational Sciences, funded by the National Science Foundation (NSF).

>>>>

\begin{abstract}
This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters. Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. Jenkins was chosen for its versatility, large user base, and multitudes of plugins including plotting test results over time. We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). Not only does Jenkins have the ability to store historical data, but it can also send email or text pages based on results of a test. Other requirements we had include two-factor authentication for accessing Jenkins GUI with administrator privileges and account management through LDAP. In this paper we describe our experience in deploying Jenkins as user-level system-wide regression testing and monitoring framework for Blue Waters.
\end{abstract}

\begin{abstract}
LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters. Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service. We evaluated test frameworks such as Inca [1] and Jenkins [2]. Jenkins was chosen for its versatility, large user base, and multitude of plugins including plotting test results over time. We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). Not only does Jenkins have the ability to store historical data but it can also send customized notifications (e.g. send email or text pages) based on the result of a test. Some of the requirements we had include two-factor authentication to access Jenkins GUI with privileges to execute tests and account management through LDAP. In this paper we describe our implementation of these requirements to ensure a secure and usable deployment of a Jenkins instance.

@@

\subsection{Introduction to Jenkins}
Jenkins [2] is a self-contained, open source automation server which can be used to automate all sorts of tasks such as building, testing, and deploying software. Jenkins can be installed through native system packages, Docker, or even run standalone by any machine with the Java Runtime Environment installed. 
To install from rpm as root for centos:
wget -O /etc/yum.repos.d/jenkins.repo http://pkg.jenkins-ci.org/redhat-stable/jenkins.repo
rpm --import https://jenkins-ci.org/redhat-stable/jenkins-ci.org.key
yum install jenkins
\subsection{Master-Node Configuration}
We added a standard user account to our cluster that will execute the Jenkins tests. Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.  The keys on the server are located in Jenkins home directory (/var/lib/jenkins/.ssh). Using the GUI management console, the keyfile location and passphrase was entered under Manage Jenkins, Configure System, SSH remote hosts section. A unique SSH site is configured for our TDS, production and development login nodes.

@@

\subsection{Configuration Choices}
Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restricting access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.  A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console. All the configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted.

\begin{lstlisting}
(Jenkins sever configuration file snippets below)
/etc/ssh/sshd_config:
Match Host bwbh1.ncsa.illinois.edu,
bwbh2.ncsa.illinois.edu
HostbasedAuthentication yes

@@

/etc/httpd/conf.d/ssl.conf:
 # -- The following sets ReverseProxy for Jenkins
  ProxyRequests       Off
  ProxyPreserveHost   On
  AllowEncodedSlashes On
  <Proxy *>
    Order deny,allow
    Allow from all
  </Proxy>
  ProxyPass       / http://localhost:8080/ nocanon
  ProxyPassReverse / http://localhost:8080/
  ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
  RequestHeader set X-Forwarded-Proto "https"
  RequestHeader set X-Forwarded-Port "443"

 # -- The following sets OTP for Jenkins SSL connection
  DefineExternalAuth pwauth+session pipe /usr/local/bin/
  pwauth+session
  <LocationMatch / > 
    AuthType Basic
    AuthBasicProvider external
    AuthName "NCSA RSA OTP login" 
    AuthExternal pwauth+session
    require valid-user

@@

  </LocationMatch>

 /usr/local/bin/pwauth+session: https://github.com/reubendb/
 BasicAuthOTPSession/blob/master/BasicAuthOTPSession.py#L1
\end{lstlisting}
\subsection{LDAP with Jenkins}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

@@

\section{Conclusion}
\subsection{reproducibility and regression testing}
\subsection{rapid reaction}
\subsection{caveats}
Transient errors with Jenkins sometimes occur--particularly with the Jenkins ssh subsystem.  It's not unusual to get failure rates of 1/100 from an ssh failure which is completely transient (immediately running the test again manually clears the issue on the dashboard).
\label{sec:conclusion}

% use section* for acknowledgement
\section*{Acknowledgment}
This research used resources at the National Institute for Computational Sciences and the National Center for Supercomputing Applications, funded by the National Science Foundation (NSF).
